\cvsection{Experience}
\begin{cventries}
%-----------------------------------------------------------------------------------
% ALUMINIUM OF GREECE INTERN
%--------------------------------------------------------------------------------
  \cventry
    {Aluminium of Greece}
    {Intern, Maintenance of Alumina, Non-Invasive Testing Methods}    
    {Viotia, Greece}
    {July. 2016 - Aug. 2016}
    {
      \begin{cvitems}
       \item {Was part of a team responsible for the optimisation and maintenance of equipment used in the production of aluminium oxide (alumina).}
       \item {Was familiarised with methods and techniques used to investigate for structural failures in industrial equipment.}
       \item {Performed non-destructive testing (e.g. Ultrasonic testing, liquid penetrant, eddy-current testing, remote visual inspection).}
       \item {Gained experience on the modus operandi of an energy power plant.}
      \end{cvitems}
    }
  	
%------------------------------------------------------------------------------------
% PRIVATE TUTORING MATHEMATICS
%------------------------------------------------------------------------------------
  \cventry
  	{Self-Employment}
		{Private Tutor}
		{Egham, UK}
		{Oct. 2015 - Nov. 2015}
		{
	 	  \begin{cvitems}
	  		\item {Organised study tutorials and provided assistance with calculus and statistics for 1st year economics students from Bocconi University.}
		  \end{cvitems}
		}
		
%------------------------------------------------------------------------------------
% GALLERY WITH... HOPE
%------------------------------------------------------------------------------------
  \cventry
    {Non-profit organisation}
    {Gallery with... ELPIDA (Hope)}
    {Athens, Greece}
    {May. 2012}
    {
      \begin{cvitems}
      	\item {Organised, with two more individuals, a 3-day art gallery focused on charity, \newline with the aid of \textit{Piraeus Bank Group Cultural Foundation} and \textit{Association of Friends and Children with Cancer ``ELPIDA”}.}
      	\item {Intent of the gallery, was to promote hope and give back to people who were in need during times of hardship.}
      	\item {152 art pieces from the 1st workshop of Athens’s Art School, were displayed, in Moraitis School, raising a total of \euro 75,000.}
      	\item {The profits were used for two purposes:\\
      	\begin{cvitems}
      	  \item[--] {Support the noble cause of the \textit{Association of Friends and Children with Cancer ``ELPIDA”} and its president’s \newline Marianna~V.~Vardinoyannis.}
      	  \item[--] {Contribute in the combat of youth unemployment by employing and promoting young artists.}
      	\end{cvitems}
        	  }
      \end{cvitems}
	}
\end{cventries}
